Automated discovery \\ of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Describe rest of constraints

\appendix
\section{Operator constraints}
\label{sec:constraints}

We implement several constraints on the space of expressions, to rule out uninterpretable combinations of operators.
We impose the following nested constraints:
\begin{enumerate}
    \item No operator with arity of 1 (i.e., taking a single argument) may be nested with another arity-1 operator, unless the operator is square.
    \begin{enumerate}
        \item However, a square can only be nested inside itself once.
    \end{enumerate}
    \item A division operator may only be nested inside itself once.
    \item A power operator may not contain any arity-1 operator, except a square.
\end{enumerate}

>>>>

\clearpage
\appendix
\section{Operator constraints}
\label{sec:constraints}

With full flexibility over how symbolic operators can be arranged up to a maximum number, surprisingly many combinations exist which are simple and accurate, yet completely uninterpretable.
Typically, a genetic algorithm might find that a particular deeply nested combination of operators might perform very well, with the overall complexity being low.
However, we wish to find a model that is interpretable, and so we provide some additional constraints here.

First, we implement limits on which operators can be nested, and how deeply.
We impose the following nested constraints:
\begin{enumerate}
    \item No operator with arity of 1 (i.e., an operator taking a single argument) may be nested with another arity-1 operator, unless the operator is square.
    \begin{enumerate}
        \item However, we permit a square to be nested inside itself once, as such a combination may be used to make a quadratic operation with few operations.
    \end{enumerate}
    \item The division operator may only be nested inside itself once.
    \item The power operator may not contain any arity-1 operator.
\end{enumerate}
We also impose the following constraints on maximum complexity within each operator:
\begin{enumerate}
    \item The power operator may only have a maximum complexity of 9 in its base, and 3 in its exponent.
    \item The division operator may have any complexity in the numerator, but a maximum complexity of 7 in the denominator.
    \item The Gauss operator may only have a maximum complexity of 11 in its argument.
    \item The conditional operator may only have a maximum complexity of 5 in its condition, and 11 in its resultant argument.
\end{enumerate}
These prevent \pysr from finding expressions which, despite being low-complexity and high-accuracy, are still uninterpretable to a human scientist due to unusual combinations of operators compared to typical expressions found throughout physics and astrophysics.
